Milk intake and risk of mortality risk

### 2020-06-08 Paperfolder/Paperfolder.Rmd
prepare to write in rstudio with latex

---
title: Full title of the paper (Capitalized)
author:
  - name: Dominik Leutnant
    affil: 1,2,\ddagger,*
    orcid: 0000-0003-3293-2315
  - name: John Doe
    affil: 2, \dagger, \ddagger
affiliation:
  - num: 1
    address: |
      Muenster University of Applied Sciences - 
      Institute for Infrastructure, Water, Resources, Environment
      Correnstr. 25, 48149 Muenster, Germany
    email: leutnant@fh-muenster.de
  - num: 2
    address: |
      Your department
      Street, City, Country
    email: mail@mail.com
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
journal: water
type: article
status: submit
bibliography: mybibfile.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
sampleavailability: |
  Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

>>>>

---
title: Milk intake and risk of mortality risk 
author:
  - name: Chaochen Wang
    affil: 1,*
    orcid: 0000-0001-5533-1497
  - name: John Doe
    affil: 2, \dagger, \ddagger
affiliation:
  - num: 1
    address: |
      Muenster University of Applied Sciences - 
      Institute for Infrastructure, Water, Resources, Environment
      Correnstr. 25, 48149 Muenster, Germany
    email: leutnant@fh-muenster.de
  - num: 2
    address: |
      Your department
      Street, City, Country
    email: mail@mail.com
# firstnote to eighthnote
firstnote: |
  Current address: Updated affiliation
secondnote: |
  These authors contributed equally to this work.
correspondence: |
  leutnant@fh-muenster.de; Tel.: +XX-000-00-0000.
journal: water
type: article
status: submit
bibliography: mybibfile.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
sampleavailability: |
  Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---
